---
title: "Ahmed Homework 3"
author: "Ahmed salem alhumaiqani- 119203007"
date: "2022-12-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# IE 421 - Case Study - Financial Index Return

```{r,message=FALSE}
library(dplyr)
library(lubridate)
library(corrplot)
library(PerformanceAnalytics)
library(ggplot2)
library(tidyr)
library(dygraphs)
library(knitr)
library(forcats)
```

```{r}
dFIR <- read.csv2("C:/Users/a7med/Downloads/dFIR.csv")
  View(dFIR)
```

```{r}
dFIR <- read.csv2("C:/Users/a7med/Downloads/dFIR.csv")
```
## Task 1. Visualizing Financial Index Returns

### 1.1 Data Import

```{r}
head(dFIR) 
dim(dFIR) 
str(dFIR) 
summary(dFIR) 
```

### 1.2 Converting Dates to Proper Format

```{r}
dFIR=dFIR %>%
  mutate(date = dmy(date))
str(dFIR)
```

### 1.3 Correlation Analysis

```{r}
cor(dFIR[,-1])
```

```{r}
c=cor(dFIR[,-1])
corrplot(c, method="circle",type="upper")
```

```{r,warning=FALSE}
chart.Correlation(dFIR[,-1])
```

### 1.4 Time Series Plots

```{r}
ggplot(dFIR, aes(x = date, y = ISE)) + 
  geom_line(color="steelblue") + labs(x="Date",y="Return",title="Istanbul Stock Exchange Daily Returns")
```

```{r}
dG <- dFIR %>% 
  select(date, ISE, SP) %>% 
  gather(key = "index", value = "value", -date) 
```

```{r}
ggplot(dG, aes(x = date, y = value)) + 
  geom_line(aes(color = index), size = 0.3) + labs(x="Date",y="Return",title="Daily Returns for ISE and S&P 500")
```

```{r}

dG <- dFIR %>%
  select(date, ISE, SP, DAX) %>%
  gather(key = "index", value = "value", -date)
ggplot(dG, aes(x = date, y = value)) + 
  geom_line(aes(color = index), size = 0.3) + labs(x="Date",y="Return",title="Daily Returns for ISE, S&P 500, DAX")
```

```{r}
dG <- dFIR %>%
  gather(key = "index", value = "value", -date)
ggplot(dG, aes(x = date, y = value)) + 
  geom_line(aes(color = index), size = 0.3,alpha=0.5) + labs(x="Date",y="Return",title="Daily Returns for All Six Indexes")
```

```{r}
ggplot(dG, aes(x = date, y = value)) + 
  geom_line(color="steelblue",size = 0.3) +
  facet_wrap(~ index, nrow = 6)
```

```{r}
d3=xts(x=dFIR[,-1],order.by=dFIR$date)
dygraph(d3) %>%
  dyRangeSelector(height = 20)
```

## Task 2. Volatility Analysis of Financial Index Returns

### 2.1 Understanding Volatility
Go back to the time series plot above, where you combine the ISE, SP and DAX returns on a single chart. Which index seems to have the highest volatility?

### 2.2 Calculating Monthly Volatility for Each Index

```{r}
d.month.volatility <- dFIR %>%
  group_by(month = cut(date, "month")) %>%
  summarize(ISE=sd(ISE),SP=sd(SP),DAX=sd(DAX),FTSE=sd(FTSE),NIKKEI=sd(NIKKEI),BOVESPA=sd(BOVESPA))
```

```{r}
head(d.month.volatility)
```

```{r}
d.month.volatility <- d.month.volatility %>% mutate(month=ymd(month))
```

```{r}
head(d.month.volatility)
```

### 2.3 Visualizing Monthly Volatility

```{r}
ggplot(d.month.volatility, aes(x = month, y = ISE)) + 
  geom_line(color="steelblue", size = 1) + labs(x="Months",y="Standard Deviation",title="Monthly Volatility of Istanbul Stock Exchange Returns")
```

```{r}
dm <- d.month.volatility %>%
  gather(key = "index", value = "value", -month)

ggplot(dm, aes(x = month, y = value)) + 
  geom_line(aes(color = index), size = 0.5) + labs(x="Months",y="Standard Deviation",title="Monthly Volatility of All Six Index Returns")
```

